---
title: "Report on diamonds data analysis"
output:
  html_document:
    df_print: paged
---

```{r setup}
library(ggplot2)
library(dplyr)
library(readr)


```

```{r}
source("./src/utils.R")
```


## Problem Statement

Understand and analyse features that effect the price of the diamonds.



## Data Ingestion

This classic dataset contains the prices and other attributes of almost 54,000 diamonds. It's a great dataset for beginners learning to work with data analysis and visualization.

Content
price price in US dollars (\$326--\$18,823)

carat weight of the diamond (0.2--5.01)

cut quality of the cut (Fair, Good, Very Good, Premium, Ideal)

color diamond colour, from J (worst) to D (best)

clarity a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))

x length in mm (0--10.74)

y width in mm (0--58.9)

z depth in mm (0--31.8)

depth total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43--79)

table width of top of diamond relative to widest point (43--95)

```{r}

diamonds <- read_csv("data/raw/diamonds.csv", 
    col_types = cols(...1 = col_skip()))
```

## Data Preprocessing

```{r}
diamonds <- diamonds %>%
  mutate_at(vars(cut, color, clarity),
            factor)
```


## Exploratory Data Analysis

### Basic statistics

```{r}
summary(diamonds)
```

```{r}
str(diamonds)
```


### `price`

```{r}
ggplot(diamonds) +
  geom_histogram(aes(x = log10(price)))
```


### Continuous vs target `price`

#### `carat` vs `price`

```{r}
tempdf <- diamonds %>%
  filter(carat < 3) %>%
  mutate(carat = log10(carat),
         price = log1p(price))
subplot_cont_cont_vars(df = tempdf,
                       predictor_var = "carat",
                       target_var = "price")



```

#### `depth` vs `price`

```{r}

tempdf <- diamonds %>%
  filter(depth > 55 & depth < 70) %>%
  mutate(price = log1p(price))
subplot_cont_cont_vars(df = tempdf,
                       predictor_var = "depth",
                       target_var = "price")

```



#### `table` vs `price`

```{r}
tempdf <- diamonds %>%
  filter(table > 50 & table < 70)
subplot_cont_cont_vars(df = tempdf,
                       predictor_var = "table",
                       target_var = "price")

```


#### `x` vs `price`

```{r}
tempdf <- diamonds %>%
  filter(table > 50 & depth < 70)
subplot_cont_cont_vars(df = diamonds,
                       predictor_var = "x",
                       target_var = "price")

```

### Discrete vs target var `price`

#### `Cut` vs `price`

```{r fig.width=10}
subplot_disc_cont_vars(df= diamonds,
                       predictor_var = "cut",
                                   target_var = "price")
```

#### `Color` vs `price`

```{r }
subplot_disc_cont_vars(df= diamonds,
                       predictor_var = "color",
                                   target_var = "price")
```



#### `clarity` vs `price`

```{r }
subplot_disc_cont_vars(df= diamonds,
                       predictor_var = "clarity",
                                   target_var = "price")
```


### More data processing

```{r}
diamonds_final <- diamonds %>%
  filter(table > 50 & table < 70) %>%
  filter(depth > 55 & depth < 70) %>%
  filter(carat <3) %>%
  mutate(price = log1p(price),
         carat = log10(carat)) %>%
  select(price, carat
         , x, cut, color, clarity)


```


### ML Modelling

```{r}
lm_model <- lm(price ~ ., data = diamonds_final)

summary(lm_model)
```




